An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-29 paper/2.minbigul.tex
update references
add no indent

minBiGUL inherited from BiGUL also supports transformations $put$ and $get$ which satisfy two above laws. In addition, we restrict adaptive cases of BiGUL on minBiGUL. Then $put$ and $get$ satisfy one more law, \textsc{PutPut} \cite{putput}, like the following:

@@

$bfoldr$ will look like a composition of many programs at some points in the evaluation if we slow down this process. Since $\circ$ has a higher priority than $\times$, it is seemingly impossible to transform $bfoldr$ from the left associative composition style to the right one.

>>>>

minBiGUL inherited from BiGUL also supports transformations $put$ and $get$ which satisfy two above laws. In addition, we restrict adaptive cases of BiGUL on minBiGUL. Then $put$ and $get$ satisfy one more law, \textsc{PutPut} \cite{Foster:2007:CBT:1232420.1232424}, like the following:

@@

\noindent $bfoldr$ will look like a composition of many programs at some points in the evaluation if we slow down this process. Since $\circ$ has a higher priority than $\times$, it is seemingly impossible to transform $bfoldr$ from the left associative composition style to the right one.
